Simulation Figures for Genome Biology (simulations)

### 2018-06-09 manuscript_figures/manuscript_figures_sims.Rmd
Add TNR plot for null; calc more stats; match other plot styles

        zz <- dplyr::group_by(zz, blabel, key, alpha)
        zz <- dplyr::summarize(zz,
                               med_value = median(value, na.rm = TRUE),
                               mean_value = mean(value, na.rm = TRUE),
                               nNA = sum(is.na(value)))
        dplyr::ungroup(zz)
    })
    names(res) <- gsub("\\.rds$", "", basename(res_files))
    saveRDS(res, summary_file)
}

@@

```{r}
res_nullset <- dplyr::filter(res, setting == "null")
res_nullset <- dplyr::mutate(res_nullset, dist = factor(dist, levels = c("gaussian", "t5", "chisq4")))
res_nullset <- tidyr::complete(res_nullset, setting, Method, dist, key)
```

@@

```{r, fig.width = 8, fig.height = 3}
dplyr::filter(res_nullset, key == "rejectprop") %>%
    filter(! (Method == "ashq" & dist == "chisq4"),
           ! (grepl("scott", Method) & dist == "chisq4")) %>%
    ggplot(aes(x = Method, y = mean_value)) +
    geom_bar(color = "black", fill = "gray", stat = "identity") +
    facet_grid(. ~ dist) +
    coord_flip() +
    scale_y_continuous("Average % Rejected Tests", breaks = seq(0, 1, .01), labels = scales::percent) +
    theme_bw() +
    ggtitle("Rejected proportion of in null simulations (average over 100 replications)") 
```

@@

```{r, fig.width = 8, fig.height = 3}
gp <- dplyr::filter(res_nullset, key == "FWER") %>%
    filter(! (Method == "ashq" & dist == "chisq4"),
           ! (grepl("scott", Method) & dist == "chisq4")) %>%
    ggplot(aes(x = Method, y = mean_value)) +
    geom_bar(color = "black", fill = "gray", stat = "identity") +
    facet_grid(. ~ dist) +
    coord_flip() +
    scale_y_continuous("FWER", breaks = seq(0, 1, .2), labels = scales::percent) +
    theme_bw() +
    ggtitle("Proportion of replications with at least one false positive (over 100 replications)")

ggsave(file.path(outdir, "FigureSsim-null.pdf"), gp, width = 8, height = 3)
```

@@

First, we look at the false discovery rate across the 100 replications.
We create the plot with a discrete color scale.

```{r, fig.width = 8, fig.height = 6}
fdr_bins <- c(0, .05, .07, .09, .11, .13, .15, .2, 1)
dplyr::filter(res_covset, key == "FDR") %>%
    dplyr::mutate(val = cut(mean_value, breaks = fdr_bins, include.lowest = TRUE)) %>%
    ggplot() +
    geom_tile(aes(x = setting, y = Method, fill = val)) +
    scale_x_discrete("Setting", expand = c(0, 0)) + 
    scale_y_discrete(expand = c(0, 0)) + 
    scale_fill_manual("FDR", values = RColorBrewer::brewer.pal(9, "PRGn")[2:9],
                      na.value = "gray50", drop = FALSE) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
    facet_grid(. ~ dist, scales = "free", space = "free", labeller= label_parsed) +
    ggtitle(paste0("Mean FDR across 100 replications (alpha = ", alpha, ")"))
```

We can create this plot with a continuous color scale as well.
However, it is incredibly hard to distinguish values if we look at the entire range of
possible values, so we will clamp them down to be between 0 and 0.2 (values above 0.2 will be
set to 0.2).

```{r, fig.width = 8, fig.height = 6}
gp_fdr <- dplyr::filter(res_covset, key == "FDR", setting != "null") %>%
    ggplot() +
    geom_tile(aes(x = setting, y = Method, fill = mean_value)) +
    scale_x_discrete("Setting", expand = c(0, 0)) + 
    scale_y_discrete(expand = c(0, 0)) + 
    scale_fill_gradient2("FDR", low = RColorBrewer::brewer.pal(6, "PRGn")[1],
                         high = RColorBrewer::brewer.pal(6, "PRGn")[6],
                         midpoint = alpha, na.value = "gray50", limits = c(0, .2),
                         oob = scales::squish) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    facet_grid(. ~ dist, scales = "free", space = "free", labeller = label_parsed) + 
    ggtitle(paste0("Mean FDR across 100 replications (alpha = ", alpha, ")"))
gp_fdr
```

We can also look at the true positive rates.

```{r, fig.width = 8, fig.height = 6}
gp_tpr <- dplyr::filter(res_covset, key == "TPR") %>%
    ggplot() +
    geom_tile(aes(x = setting, y = Method, fill = mean_value)) +
    scale_x_discrete("Setting", expand = c(0, 0)) + 
    scale_y_discrete(expand = c(0, 0)) + 
    scale_fill_distiller("TPR", palette = "Blues", limits = c(0, 1), direction = 1) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    facet_grid(. ~ dist, scales = "free", space = "free", labeller = label_parsed) + 
    ggtitle(paste0("Mean TPR across 100 replications (alpha = ", alpha, ")"))
gp_tpr
```

Alternatively, rather than using heatmaps, we can use scatterplots to look at these values.

```{r, fig.width = 7, fig.height = 6}
## looking at FDR vs TPR
col <- as.character(res_covset$col)
names(col) <- as.character(res_covset$Method)

dplyr::select(res_covset, Method, setting, dist, key, mean_value, col, lty) %>%
    dplyr::filter(key %in% c("FDR", "TPR")) %>%
    tidyr::spread(key, mean_value) %>%
    ggplot(aes(x = FDR, y = TPR, color = Method)) +
    geom_point(alpha = 1/2) +
    scale_color_manual(values = col) +
    facet_grid(dist ~ setting, labeller = labeller(dist = label_parsed)) +
    theme_bw()

## looking at noninformative vs. informative (cubic)
dplyr::select(res_covset, Method, setting, dist, key, mean_value) %>%
    dplyr::filter(setting %in% c("noninformative", "informative-cubic"),
                  key %in% c("TPR"),
                  ! Method %in% c("ashq", "bonf")) %>%
    tidyr::spread(setting, mean_value) %>%
    ggplot(aes(x = noninformative, y = `informative-cubic`, color = Method)) +
    geom_point(alpha = 1/2) +
    scale_color_manual(values = col) +
    facet_wrap( ~ dist, nrow = 1, scales = "free", labeller = labeller(dist = label_parsed)) +
    theme_bw() +
    scale_x_continuous(labels = scales::percent) + 
    scale_y_continuous(labels = scales::percent) + 
    geom_abline(color = "blue", lty = 2, alpha = 1/3) +
    ggtitle("Mean TPR for Informative and Noninformative Simulations")

## looking at noninformative vs. informative (cubic)
pfdr <- dplyr::select(res_covset, Method, setting, dist, key, mean_value) %>%
    dplyr::filter(setting %in% c("noninformative", "informative-cubic"),
                  key %in% c("FDR")) %>%
    tidyr::spread(setting, mean_value) %>%
    ggplot(aes(x = noninformative, y = `informative-cubic`, color = Method)) +
    geom_abline(color = "blue", lty = 2, alpha = 1/3) +
    geom_vline(xintercept = 0.10, color = "red", lty = 2, alpha = 1/3) +
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) +
    geom_point(alpha = 1/2) +
    scale_color_manual(values = col) +
    facet_wrap( ~ dist, nrow = 2, scales = "free", labeller = labeller(dist = label_parsed)) +
    theme_bw() +
    scale_x_continuous("FDR w/ Noninformative Covariate", labels = scales::percent, limits = c(0, 1)) + 
    scale_y_continuous("FDR w/ Informative Covariate (cubic)", labels = scales::percent, limits = c(0, 1)) + 
    ggtitle("Mean FDR for Informative and Noninformative Simulations")

## looking at noninformative vs. informative (cubic)
ptpr <- dplyr::select(res_covset, Method, setting, dist, key, mean_value) %>%
    dplyr::filter(setting %in% c("noninformative", "informative-cubic"),
                  key %in% c("TPR")) %>%
    tidyr::spread(setting, mean_value) %>%
    ggplot(aes(x = noninformative, y = `informative-cubic`, color = Method)) +
    geom_abline(color = "blue", lty = 2, alpha = 1/3) +
    geom_vline(xintercept = 0.10, color = "red", lty = 2, alpha = 1/3) +
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) +
    geom_point(alpha = 1/2) +
    scale_color_manual(values = col) +
    facet_wrap( ~ dist, nrow = 2, scales = "free", labeller = labeller(dist = label_parsed)) +
    theme_bw() +
    scale_x_continuous("TPR w/ Noninformative Covariate", labels = scales::percent, limits = c(0, 1)) + 
    scale_y_continuous("TPR w/ Informative Covariate (cubic)", labels = scales::percent, limits = c(0, 1)) + 
    ggtitle("Mean TPR for Informative and Noninformative Simulations") 
```

@@

```{r, fig.width = 11, fig.height = 4.5}
plot_grid(pfdr, ptpr)

@@

ggsave(file.path(outdir, "FigureSsim-noise.pdf"), gp, width = 11, height = 4.5)
```

@@

```{r, fig.width = 8, fig.height = 10}
## looking at FDR vs TPR
col <- as.character(res_pi0set$col)
names(col) <- as.character(res_pi0set$Method)
lty <- as.character(res_pi0set$lty)
names(lty) <- as.character(res_pi0set$Method)

pfdr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, col, lty) %>%
    dplyr::filter(key == "FDR") %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_point(alpha = 1/2, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    theme_bw() +
    facet_grid(setting ~ .) + 
    ggtitle("Average FDR Across Varying Null Proportion")
pfdr

pfdr + coord_cartesian(ylim = c(0, .25))

ptpr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, col, lty) %>%
    dplyr::filter(key == "TPR") %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_point(alpha = 1/2, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    theme_bw() +
    facet_grid(setting ~ .) + 
    ggtitle("Average TPR Across Varying Null Proportion")
ptpr
```

@@

```{r, fig.width = 10, fig.height = 5}
gp <- plot_grid(pfdr + coord_cartesian(ylim = c(0, .25)) + guides(color = FALSE, linetype = FALSE),
                ptpr, rel_widths = c(1, 1.25), labels = LETTERS[1:2])
gp
ggsave(file.path(outdir, "FigureSsim-nullprop.pdf"), gp, width = 10, height = 5)
```

@@

```{r, fig.width = 8, fig.height = 5}
## looking at FDR vs TPR
col <- as.character(res_unimodal$col)
names(col) <- as.character(res_unimodal$Method)
lty <- as.character(res_unimodal$lty)
names(lty) <- as.character(res_unimodal$Method)

uniplot <- dplyr::select(res_unimodal, Method, dist, signal, key, mean_value, col, lty) %>%
    dplyr::filter(key %in% c("FDR", "TPR")) %>%
    tidyr::spread(key, mean_value) %>%
    ggplot(aes(x = TPR, y = FDR, color = Method)) +
    geom_point(alpha = 1/2) +
    scale_color_manual(values = col) +
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("TPR", labels = scales::percent, breaks = seq(0, 1, .2)) + 
    scale_y_continuous("FDR", labels = scales::percent, breaks = seq(0, 1, .2)) + 
    theme_bw() +
    facet_grid(signal ~ dist, labeller = labeller(dist = label_parsed)) + 
    ggtitle("Average FDR and TPR Across Unimodal Settings")
uniplot

ggsave(file.path(outdir, "FigureSsim-unimodal.pdf"), uniplot, width = 8, height = 5)
```

@@

pfdr <- dplyr::select(res_infoset, Method, setting, level, key, mean_value, col, lty) %>%
    dplyr::filter(key == "FDR") %>%
    ggplot(aes(x = level / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_point(alpha = 1/2, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Informativeness", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    theme_bw() +
    facet_grid(setting ~ .) + 
    ggtitle("Average FDR Across Varying Informativeness")
pfdr

ptpr <- dplyr::select(res_infoset, Method, setting, level, key, mean_value, col, lty) %>%
    dplyr::filter(key == "TPR") %>%
    ggplot(aes(x = level / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_point(alpha = 1/2, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Informativeness", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    theme_bw() +
    facet_grid(setting ~ ., scales = "free_y") + expand_limits(y = 0) +
    ggtitle("Average TPR Across Varying Informativeness")
ptpr
```

@@

```{r, fig.width = 10, fig.height = 5}
gp <- plot_grid(pfdr + guides(color = FALSE, linetype = FALSE), ptpr,
          rel_widths = c(1, 1.25), labels = LETTERS[1:2])
gp

ggsave(file.path(outdir, "FigureSsim-informativeness.pdf"), gp, width = 10, height = 5)
```

>>>>

        zz <- dplyr::group_by(zz, blabel, key, alpha)
        zz <- dplyr::summarize(zz,
                               se = sd(value, na.rm = TRUE) / sqrt(sum(!is.na(value))),
                               q10 = quantile(value, .1, na.rm = TRUE),
                               q90 = quantile(value, .9, na.rm = TRUE),
                               med_value = median(value, na.rm = TRUE),
                               mean_value = mean(value, na.rm = TRUE),
                               nNA = sum(is.na(value)))
        dplyr::ungroup(zz)
    })
    names(res) <- gsub("\\.rds$", "", basename(res_files))
    saveRDS(res, summary_file)
}

@@

```{r}
res_nullset <- dplyr::filter(res, setting == "null")
res_nullset <- dplyr::mutate(res_nullset, dist = factor(dist, levels = c("gaussian", "t5", "chisq4")))
res_nullset <- tidyr::complete(res_nullset, setting, Method, dist, key)

col <- as.character(res_nullset$col)
names(col) <- as.character(res_nullset$Method)
```

@@

```{r, fig.width = 8, fig.height = 5}
dplyr::filter(res_nullset, key == "rejectprop") %>%
    filter(! (Method == "ashq" & dist == "chisq4"),
           ! (grepl("scott", Method) & dist == "chisq4")) %>%
    ggplot(aes(x = Method, y = mean_value, color = Method)) +
    geom_point() +
    facet_grid(. ~ dist) +
    scale_color_manual(values = col, guide = FALSE) +
    scale_y_continuous("Average % Rejected Tests", breaks = seq(0, 1, .01), labels = scales::percent) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    ggtitle("Rejected proportion of in null simulations (average over 100 replications)") 
```

@@

```{r, fig.width = 8, fig.height = 5}
dplyr::filter(res_nullset, key == "FWER") %>%
    filter(! (Method == "ashq" & dist == "chisq4"),
           ! (grepl("scott", Method) & dist == "chisq4")) %>%
    ggplot(aes(x = Method, y = mean_value, color = Method)) +
    geom_point() +
    scale_color_manual(values = col, guide = FALSE) +
    facet_grid(. ~ dist) +
    scale_y_continuous("FWER", breaks = seq(0, 1, .2), labels = scales::percent) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    ggtitle("Proportion of replications with at least one false positive (over 100 replications)") 
```

Finally, we plot the TNR as was done for the yeast in silico experiments/simulations.

```{r, fig.width = 8, fig.height = 5}
gp <- dplyr::filter(res_nullset, key == "TNR") %>%
    filter(! (Method == "ashq" & dist == "chisq4"),
           ! (grepl("scott", Method) & dist == "chisq4")) %>%
    ggplot(aes(x = Method, y = mean_value, color = Method)) +
    geom_point() +
    facet_grid(. ~ dist) +
    scale_y_continuous("TPR", labels = scales::percent) +
    scale_color_manual(values = col, guide = FALSE) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    ggtitle("Average TNR (over 100 replications)") 
gp

ggsave(file.path(outdir, "FigureSsim-null.pdf"), gp, width = 8, height = 5)
```

@@

We use scatterplots to look at the FDR and TPR values.

```{r, fig.width = 11, fig.height = 4.5}
## looking at FDR vs TPR
col <- as.character(res_covset$col)
names(col) <- as.character(res_covset$Method)

## looking at noninformative vs. informative (cubic)
dplyr::select(res_covset, Method, setting, dist, key, mean_value) %>%
    dplyr::filter(setting %in% c("noninformative", "informative-cubic"),
                  key %in% c("TPR"),
                  ! Method %in% c("ashq", "bonf")) %>%
    tidyr::spread(setting, mean_value) %>%
    ggplot(aes(x = noninformative, y = `informative-cubic`, color = Method)) +
    geom_point(alpha = 1) +
    scale_color_manual(values = col) +
    facet_wrap( ~ dist, nrow = 1, scales = "free", labeller = labeller(dist = label_parsed)) +
    scale_x_continuous(labels = scales::percent) + 
    scale_y_continuous(labels = scales::percent) + 
    geom_abline(color = "blue", lty = 2, alpha = 1/3) +
    ggtitle("Mean TPR for Informative and Noninformative Simulations") 
```

```{r}
## looking at noninformative vs. informative (cubic)
pfdr <- dplyr::select(res_covset, Method, setting, dist, key, mean_value) %>%
    dplyr::filter(setting %in% c("noninformative", "informative-cubic"),
                  key %in% c("FDR")) %>%
    tidyr::spread(setting, mean_value) %>%
    ggplot(aes(x = noninformative, y = `informative-cubic`, color = Method)) +
    geom_abline(color = "blue", lty = 2, alpha = 1/3) +
    geom_vline(xintercept = 0.10, color = "red", lty = 2, alpha = 1/3) +
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) +
    geom_point(alpha = 1) +
    scale_color_manual(values = col) +
    facet_wrap( ~ dist, nrow = 2, scales = "free", labeller = labeller(dist = label_parsed)) +
    scale_x_continuous("FDR w/ Noninformative Covariate", labels = scales::percent, limits = c(0, 1)) + 
    scale_y_continuous("FDR w/ Informative Covariate (cubic)", labels = scales::percent, limits = c(0, 1)) + 
    ggtitle("FDR (Informative and Noninformative Sims)")

## looking at noninformative vs. informative (cubic)
ptpr <- dplyr::select(res_covset, Method, setting, dist, key, mean_value) %>%
    dplyr::filter(setting %in% c("noninformative", "informative-cubic"),
                  key %in% c("TPR")) %>%
    tidyr::spread(setting, mean_value) %>%
    ggplot(aes(x = noninformative, y = `informative-cubic`, color = Method)) +
    geom_abline(color = "blue", lty = 2, alpha = 1/3) +
    geom_vline(xintercept = 0.10, color = "red", lty = 2, alpha = 1/3) +
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) +
    geom_point(alpha = 1) +
    scale_color_manual(values = col) +
    facet_wrap( ~ dist, nrow = 2, scales = "free", labeller = labeller(dist = label_parsed)) +
    scale_x_continuous("TPR w/ Noninformative Covariate", labels = scales::percent, limits = c(0, 1)) + 
    scale_y_continuous("TPR w/ Informative Covariate (cubic)", labels = scales::percent, limits = c(0, 1)) + 
    ggtitle("TPR (Informative and Noninformative Sims)") 
```

@@

```{r, fig.width = 15, fig.height = 7.5}
plot_grid(pfdr + guides(color = FALSE, linetype = FALSE), ptpr)

@@

ggsave(file.path(outdir, "FigureSsim-noise.pdf"), gp, width = 15, height = 7.5)
```

@@

```{r}
## looking at FDR vs TPR
col <- as.character(res_pi0set$col)
names(col) <- as.character(res_pi0set$Method)
lty <- as.character(res_pi0set$lty)
names(lty) <- as.character(res_pi0set$Method)

pfdr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, col, lty) %>%
    dplyr::filter(key == "FDR") %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average FDR Across Varying Null Proportion")

ptpr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, col, lty) %>%
    dplyr::filter(key == "TPR") %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average TPR Across Varying Null Proportion")
```

@@

```{r, fig.width = 15, fig.height = 7.5}
plot_grid(pfdr + guides(color = FALSE, linetype = FALSE),
          ptpr, rel_widths = c(1, 1.25), labels = LETTERS[1:2])

## trimmed ranges
gp <- plot_grid(pfdr + coord_cartesian(ylim = c(0, .25)) + guides(color = FALSE, linetype = FALSE),
                ptpr, rel_widths = c(1, 1.25), labels = LETTERS[1:2])
gp

ggsave(file.path(outdir, "FigureSsim-nullprop.pdf"), gp, width = 15, height = 7.5)
```

@@

```{r, fig.width = 12, fig.height = 7.5}
## looking at FDR vs TPR
col <- as.character(res_unimodal$col)
names(col) <- as.character(res_unimodal$Method)
lty <- as.character(res_unimodal$lty)
names(lty) <- as.character(res_unimodal$Method)

uniplot <- dplyr::select(res_unimodal, Method, dist, signal, key, mean_value, col, lty) %>%
    dplyr::filter(key %in% c("FDR", "TPR")) %>%
    tidyr::spread(key, mean_value) %>%
    ggplot(aes(x = TPR, y = FDR, color = Method)) +
    geom_point(alpha = 1) +
    scale_color_manual(values = col) +
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("TPR", labels = scales::percent, breaks = seq(0, 1, .2)) + 
    scale_y_continuous("FDR", labels = scales::percent, breaks = seq(0, 1, .2)) + 
    facet_grid(signal ~ dist, labeller = labeller(dist = label_parsed)) + 
    ggtitle("Average FDR and TPR Across Unimodal Settings")
uniplot

ggsave(file.path(outdir, "FigureSsim-unimodal.pdf"), uniplot, width = 12, height = 7.5)
```

@@

pfdr <- dplyr::select(res_infoset, Method, setting, level, key, mean_value, col, lty) %>%
    dplyr::filter(key == "FDR") %>%
    ggplot(aes(x = level / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Informativeness", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average FDR Across Varying Informativeness")
pfdr

ptpr <- dplyr::select(res_infoset, Method, setting, level, key, mean_value, col, lty) %>%
    dplyr::filter(key == "TPR") %>%
    ggplot(aes(x = level / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Informativeness", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    facet_grid(setting ~ ., scales = "free_y") + expand_limits(y = 0) +
    ggtitle("Average TPR Across Varying Informativeness")
ptpr
```

@@

```{r, fig.width = 15, fig.height = 7.5}
gp <- plot_grid(pfdr + guides(color = FALSE, linetype = FALSE), ptpr,
          rel_widths = c(1, 1.25), labels = LETTERS[1:2])
gp

ggsave(file.path(outdir, "FigureSsim-informativeness.pdf"), gp, width = 15, height = 7.5)
```
